Recursive Neural Network Part-of-Speech Tagger

### 2013-12-21 paper/paper.tex

>>>>

\paragraph{Manually Extended Embeddings}
From the anaysis of Section ~\ref{sec:confm} and also the results in Section ~\ref{sec:modelcomp}, we see that because the disappear of capitalization information of words, the RNN model is bad at telling NN and NNP. So we think we can manually extend the embeddings of words by some human made features like captitalized or not, even suffix information. This, in our view will definitely improve the performance of model a lot.
